A Parallel, Backjumping Subgraph Isomorphism Algorithm using Supplemental Graphs

### 2015-09-05 talk/talk.tex
Tweaks

\newcommand*\circled[1]{\tikz[baseline=(char.base)]{
            \node[shape=circle,draw,inner sep=0pt] (char) {#1};}}

@@

\title[A Parallel, Backjumping Subgraph Isomorphism Algorithm using Supplemental Graphs]
    {A Parallel, Backjumping Subgraph Isomorphism Algorithm using Supplemental Graphs}
\author{Ciaran McCreesh and Patrick Prosser}

@@

\begin{frame}{Applications}
    \begin{itemize}
        \item Bioinformatics and chemistry.
        \item Computer vision and pattern recognition.
        \item Fraud detection and law enforcement.
        \item Model checking.
        \item Social network analysis.
        \item Diseased cows.
    \end{itemize}
\end{frame}

@@

\section{Our Algorithm}
\frame{\sectionpage}

\begin{frame}{Our Approach}
    \begin{itemize}
        \item \textcolor{uofgrose}{Cheaper inference}: $10^4$ to $10^6$ recursive calls per second.
        \item Expensive \textcolor{uofgrose}{preprocessing once} at the top of search, rather
            than computing distances and degree sequences during search.
        \item FC-CBJ instead of MAC:
            \begin{itemize}
                \item A \textcolor{uofgrose}{counting-based all-different} propagator, which does more
                    than pairwise-$\ne$ AC but less than GAC.
                \item CBJ \textcolor{uofgrose}{without explicit conflict sets}, and without modifying propagators.
            \end{itemize}
        \item \textcolor{uofgrose}{Bit-parallelism} for all major operations.
        \item \textcolor{uofgrose}{Thread-parallel} search:
            \begin{itemize}
                \item Safe, deterministic search via nested parallel folds.
                \item Explicit early work-stealing, to fake discrepancy search.
            \end{itemize}
    \end{itemize}
\end{frame}

@@

\begin{frame}{Sequential Experiments}
    \begin{itemize}
        \item Dual Intel Xeon E5-2640 v2 (Q3'13), 64GBytes RAM. Our code is C++, LAD and VFLib are C, SND is Java.

@@

\begin{frame}{Cumulative Instances Solved}
    \only<1>{
        \input{gen-graph-cumulative-0}
    }
    \only<2>{
        \input{gen-graph-cumulative-1}
    }
    \only<3>{
        \input{gen-graph-cumulative-2}
    }
    \only<4>{
        \input{gen-graph-cumulative-3}
    }
    \only<5>{
        \input{gen-graph-cumulative-4}
    }
    \only<6>{
        \input{gen-graph-cumulative-5}
    }
\end{frame}

\begin{frame}{Versus Virtual Best Other Solver}
    \only<1>{
        \input{gen-graph-best-other-0}
    }
    \only<2>{
        \input{gen-graph-best-other-1}
    }
\end{frame}

\begin{frame}{Backjumping?}
    \only<1>{
        \input{gen-graph-backjumping-0}
    }
    \only<2>{
        \input{gen-graph-backjumping-1}
    }
\end{frame}

\begin{frame}{Counting All-Different?}
    \only<1>{
        \input{gen-graph-fad-0}
    }
    \only<2>{
        \input{gen-graph-fad-1}
    }
    \only<3>{
        \input{gen-graph-fad-2}
    }
\end{frame}

\section{Thread Parallelism}
\frame{\sectionpage}

\begin{frame}{Parallel Preprocessing}
    \begin{itemize}
        \item Entirely (mostly\ldots) routine and not very interesting, but good at offsetting the
            cost of supplemental graph construction.
    \end{itemize}
\end{frame}

@@

    \only<2> {
        \begin{itemize}
            \item Explicit \textcolor{uofgrose}{early-first work stealing}, to offset incorrect
                decisions early in search.
                \begin{itemize}
                    \item There are EHPs, and this gets rid of them more cheaply than discrepancy
                        searches.
                \end{itemize}
            \item Backjumping is a nested parallel fold with left-zero elements.
            \item Speculative, so we should \textcolor{uofgrose}{not expect linear speedups} (even
                on unsat instances).
        \end{itemize}
    }
\end{frame}

\begin{frame}{Sidenote on Safety, Parallelism, and Benchmarking}
    \begin{itemize}
        \item The way we do parallelism guarantees:
            \begin{itemize}
                \item Parallel search will \textcolor{uofgrose}{never be substantially worse} than
                    sequential search.
                \item Adding more cores will never make things substantially worse (excluding
                    hardware weirdness).
                \item Running it twice will give more or less the same runtimes.
            \end{itemize}
        \item All comparisons are against a dedicated sequential implementation of a strong
            algorithm, not a threaded implementation run with one thread.
    \end{itemize}
\end{frame}

@@

\begin{frame}{Speedups}
    \only<1>{
        \input{gen-graph-speedup-0}
    }
    \only<2>{
        \input{gen-graph-speedup-1}
    }
\end{frame}

@@

\begin{frame}{Cumulative Instances Solved}
    \only<1>{
        \input{gen-graph-cumulative-4}
    }
    \only<2>{
        \input{gen-graph-cumulative-6}
    }
    \only<3>{
        \input{gen-graph-cumulative-7}
    }
\end{frame}

\begin{frame}{Versus Virtual Best Other Solver}
    \only<1>{
        \input{gen-graph-best-other-1}
    }
    \only<2>{
        \input{gen-graph-best-other-2}
    }
\end{frame}

\section{Future Work}
\frame{\sectionpage}

@@

>>>>

@@

\title[A Parallel, Backjumping Subgraph Isomorphism Algorithm using Supplemental Graphs]
    {A Parallel, Backjumping Subgraph Isomorphism Algorithm using Supplemental Graphs}
\author[Ciaran McCreesh and Patrick Prosser]{\textbf{Ciaran McCreesh} and Patrick Prosser}

@@

\begin{frame}{Applications}
    \begin{itemize}
        \item Bioinformatics and chemistry.
        \item Computer vision and pattern recognition.
        \item Fraud detection and law enforcement.
        \item Model checking.
        \item Social network analysis.
        \item Code generation in compilers.
        \item Diseased cows.
    \end{itemize}
\end{frame}

@@

\section{Our Algorithm}

\begin{frame}{Our Approach}
    \begin{itemize}
        \item \textcolor{uofgrose}{Cheaper inference}: $10^4$ to $10^6$ recursive calls per second.
        \item Expensive \textcolor{uofgrose}{preprocessing once} at the top of search, rather
            than computing distances and degree sequences during search.
        \item FC-CBJ instead of MAC.
        \item A \textcolor{uofgrose}{counting-based all-different} propagator, which does more
            than pairwise-$\ne$ AC but less than GAC.
        \item \textcolor{uofgrose}{Bit-parallelism} for all major operations.
        \item \textcolor{uofgrose}{Thread-parallel} search.
    \end{itemize}
\end{frame}

@@

\section{Sequential Experiments}

\begin{frame}{Experimental Setup}
    \begin{itemize}
        \item Dual Intel Xeon E5-2640 v2 (Q3'13), 64GBytes RAM. Our code is C++, LAD and VFLib are C, SND is Java.

@@

\begin{frame}[t,plain]{Cumulative Instances Solved}
    \only<1>{
        \input{gen-graph-cumulative-0}
    }
    \only<2>{
        \input{gen-graph-cumulative-1}
    }
    \only<3>{
        \input{gen-graph-cumulative-2}
    }
    \only<4>{
        \input{gen-graph-cumulative-3}
    }
    \only<5>{
        \input{gen-graph-cumulative-4}
    }
    \only<6>{
        \input{gen-graph-cumulative-5}
    }
\end{frame}

\begin{frame}[t,plain]{Versus Virtual Best Other Solver}
    \only<1>{
        \input{gen-graph-best-other-0}
    }
    \only<2>{
        \input{gen-graph-best-other-1}
    }
\end{frame}

\begin{frame}[t,plain]{Backjumping?}
    \only<1>{
        \input{gen-graph-backjumping-0}
    }
    \only<2>{
        \input{gen-graph-backjumping-1}
    }
\end{frame}

\begin{frame}[t,plain]{Counting All-Different?}
    \only<1>{
        \input{gen-graph-fad-0}
    }
    \only<2>{
        \input{gen-graph-fad-1}
    }
    \only<3>{
        \input{gen-graph-fad-2}
    }
\end{frame}

\section{Thread Parallelism}

\begin{frame}{Parallel Preprocessing}
    \begin{itemize}
        \item Constructing supplemental graphs is expensive, but we have lots of cores.
        \item Parallelising the loops is entirely (mostly\ldots) routine and not very interesting,
            but good at offsetting the cost of supplemental graph construction.
    \end{itemize}
\end{frame}

@@

    \only<2> {
        \begin{itemize}
            \item Explicit \textcolor{uofgrose}{deterministic early-first work stealing}, to offset
                incorrect decisions early in search.
                \begin{itemize}
                    \item There are EHPs, and this gets rid of them more cheaply than discrepancy
                        searches.
                \end{itemize}
            \item Backjumping is a nested parallel fold with left-zero elements.
            \item Speculative, so we should \textcolor{uofgrose}{not expect linear speedups} (even
                on unsat instances).
        \end{itemize}
    }
\end{frame}

\begin{frame}{Sidenote on Safety, Parallelism, and Benchmarking}
    \begin{itemize}
        \item All comparisons are against a dedicated sequential implementation of a strong
            algorithm, not a threaded implementation run with one thread.
        \item The way we do parallelism guarantees:
            \begin{itemize}
                \item Parallel search will \textcolor{uofgrose}{never be substantially worse} than
                    sequential search.
                \item Adding more cores will never make things substantially worse (excluding
                    hardware weirdness).
                \item Running it twice will give more or less the same runtimes.
            \end{itemize}
    \end{itemize}
\end{frame}

@@

\begin{frame}[t,plain]{Speedups}
    \only<1>{
        \input{gen-graph-speedup-0}
    }
    \only<2>{
        \input{gen-graph-speedup-1}
    }
\end{frame}

@@

\begin{frame}[t,plain]{Cumulative Instances Solved}
    \only<1>{
        \input{gen-graph-cumulative-4}
    }
    \only<2>{
        \input{gen-graph-cumulative-6}
    }
    \only<3>{
        \input{gen-graph-cumulative-7}
    }
\end{frame}

\begin{frame}[t,plain]{Versus Virtual Best Other Solver}
    \only<1>{
        \input{gen-graph-best-other-1}
    }
    \only<2>{
        \input{gen-graph-best-other-2}
    }
\end{frame}

\section{Future Work}

@@

        \item Caching supplemental targets (graph databases) or patterns (code generation, kidney
            exchange).
